---
title: "Netflix - Data Analysis and variables analysis impacting on Netflix TV Show / Movie duration"
author: "Miriam Pavón Buenache"
date: "08/04/2021"
output:
  html_document:
    theme: flatly
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## <a name="top"></a>Overview

This dataset consists of tv shows and movies available on Netflix as of 2021. The dataset is collected from Flixable which is a third-party Netflix search engine.

Since the data has information about the year of its release, the director, duration, director, name of the movie etc, I would be working on these aspects to analyze what are the variables that affects the duration of a movie and the number of seasons of a TV Show.

Also, I will complete a general analysis. 


### Scope & Out of Scope
- Scope: Data analysis of the current data-set: genres, countries, cast, director, time duration, release year, added year, type of content (TV Show or movie)

- Out of scope: uses variables and data from others data-set

### Research Questions

Some of the main questions I will try to answer are: 

1.  What is the percentage of TV Shows and Movies in Netflix?
2.  What are the top 10 countries creating content for TV Shows and Movies?
3.  What are the top directors on Netflix?
4.  What is the trend of TV Shows and Movies over the years?
5.  What is the distribution of duration of the seasons in TV Shows and the duration of movies?
6.  What are the Top 10 long lasting movies in Netflix? What are the top 10 long lasting Tv Shows in Netflix?
7. Is there a relationship between the country and the movie duration?
8. Is there a relationship between the country and the number of seasons?
9. Is there a relationship between the Release Year and Duration in Movies? And the number of seasons?
10. Is there a relationship between the genre and Duration in Movies? And the number of seasons?


Click on links here to quickly view tasks completed in this assignment:

1.  [Packages Required](#point-1) 
2.  [Import Data](#point-2)
3.  [Data Preparation](#point-3) 
4.  [Data Cleaning](#point-4) 
5.  [Exploratory Data Analysis](#point-5)
6.  [Inference](#point-6)
7.  [Conclusions](#point-7) 


### <a name="point-1"></a>1.    Packages Required

```{r load-packages, message = FALSE}
# load libraries
library(tidyverse)
library(dplyr)
library(ggthemes)
library(DT)
library(lubridate)
library(nortest)
```
### <a name="point-2"></a>2.    Import Data
The data can be found here: 
https://www.kaggle.com/shivamb/netflix-show

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

data <- read.csv("netflix_titles.csv")
```

### <a name="point-3"></a>3.    Data Preparation

#### 3.1. Variables

In the dataset there are 7787 observations of 12 following variables describing the tv shows and movies:

- show_id - Unique ID for every Movie / Tv Show
- type - Identifier - A Movie or TV Show
- title - Title of the Movie / Tv Show
- rating - TV Rating of the movie / show
- director - Director of the Movie
- cast - Actors involved in the movie / show
- country - Country where the movie / show was produced
- date_added - Date it was added on Netflix
- release_year - Actual Release year of the move / show
- duration - Total Duration - in minutes or number of seasons
- listed_in - Genere
- description - The summary description

#### 3.2 Data Peculiarities

- Total "" values in countries are 502
- Total "" values in rating are 7
- Total "" values in cast are 718
- Total "" values in date_added are 10
- Total "" values in director are 2389
- Total NA values are 0
- The data has special character (Â, Aº, etc) in the title, director, cast and description
- The data_added variable needs to be converted from character to an appropriate POSIXct format

### <a name="point-4"></a>4.    Data Cleaning

#### 4.1 Missing Values

The missing values for the variables director, rating, cast, country, date_added can not be easily approximated, so for now we are going to continue without filling them. We are going to drop the missing values, at point where it will be necessary. 

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

data <- data %>%
  mutate(country = replace(country, country ==  "", NA ))

colSums(is.na(data))

data_without_countryNA <- data %>% 
  drop_na()
colSums(is.na(data_without_countryNA))
```

#### 4.2 Duplicated values
We also drop duplicated rows in the dataset based on the title, country, type, release_year variables.

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

data <- distinct(data,title,country,type,release_year, .keep_all= TRUE)
```

#### 4.3 Removing Special Characters

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
data$director <- iconv(data$director, 'utf-8', 'ASCII//TRANSLIT', sub='')
data$title <- iconv(data$title, 'utf-8', 'ASCII//TRANSLIT', sub='')
data$cast <- iconv(data$cast, 'utf-8', 'ASCII//TRANSLIT', sub='')
data$description <- iconv(data$description, 'utf-8', 'ASCII//TRANSLIT', sub='')
data$date_added <- parse_date_time(data$date_added, orders = "mdy")
```

#### 4.4 Cleaned Dataset

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
data %>%
  select(show_id, type, title, director, cast, country, date_added, release_year, rating, duration, listed_in, description)%>%
datatable(extensions = 'Buttons', options = list(dom = 'Bfrtip', buttons = I('colvis')))
```

### <a name="point-5"></a>5.    Data Analysis

#### 5.1 What is the percentage of TV Shows and Movies in Netflix?


```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph1 <- data %>% 
  group_by(type) %>% 
  summarise(Total = n())
graph1

```

```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
Var1 <-  graph1$Total/sum(graph1$Total) * 100
```
```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
ggplot(graph1, aes(x="", y=Total, fill=type)) + 
  geom_bar(stat="identity", width=1) +
  coord_polar("y") +
  theme_void() +
  ggtitle("Netflix", "Count TV Shows and Movies") +
  labs(x = "", y = "", fill = "Type")+
geom_text(aes(label=paste0(sprintf("%0.1f", round(Var1, digits = 3)), "%")), 
              size=4,
              color="white",
              position = position_stack(vjust = 0.5))
```


<p style = 'color : teal;font-size:18px'><u>Insights </u></p>

Based on the table and the graph we can see that Netflix has more than 2 times more Movies than TV Shows. The 69,1% of the content from Netflix are movies and the 30.9% are TV Shows

#### 5.2 What are the top 10 countries creating content for TV Shows and Movies?

- *TV Shows*
```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
data_without_countryNA <- distinct(data_without_countryNA,title,country,type,release_year, .keep_all= TRUE)
```
```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph2 <- data_without_countryNA %>% 
  group_by(country) %>% 
  filter (type== "TV Show") %>% 
  summarise(Total = n())  %>%
  arrange(desc(Total))
```

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph2 <- graph2 %>% 
  top_n(10) %>%
  ggplot(aes(x = reorder(country, Total), y = Total)) +
  geom_col(fill = "#5dc1b9") +
  coord_flip() +
  ggtitle("Netflix", "Top 10 countries creating TV Show Content") +
  geom_label(aes(x = reorder(country, Total), y = Total, label = Total)) +
  labs(x = "Country", y = "Total TV shows created") +
  theme_minimal()
  
graph2
```


- *Movies*

```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph3 <- data_without_countryNA %>% 
  group_by(country) %>% 
  filter (type== "Movie") %>% 
  summarise(Total = n())  %>%
  arrange(desc(Total))
```

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

graph3 <- graph3 %>% 
  top_n(10) %>%
  ggplot(aes(x = reorder(country, Total), y = Total)) +
  geom_col(fill = "#5dc1b9") +
  coord_flip() +
  ggtitle("Netflix", "Top 10 countries creating Movies") +
  geom_label(aes(x = reorder(country, Total), y = Total, label = Total)) +
  labs(x = "Country", y = "Total Movies created") +
  theme_minimal()
  
graph3
```

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>

This is a plot for the top 10 countries for the movies and TV Shows

Clearly, United States is the most favorite country to produce Netflix content for movies and TV Shows


#### 5.3 What are the top directors on Netflix (TV Shows & Movies)?
```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
dir20 <- strsplit(data$director, split = ", ")
titles_director <-  data.frame(type= rep(data$type, sapply(dir20, length)), director = unlist(dir20))
titles_director$director <- as.character(gsub(","," ", titles_director$director))
```

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph4 <- na.omit(titles_director) %>% 
  filter(!is.na(director) & !director == "") %>%
  group_by(director) %>% 
  filter (type== "Movie") %>% 
  summarise(Total = n())  %>%
  arrange(desc(Total))

graph4

graph4 <- graph4 %>%
  top_n(10) %>%
  ggplot(aes(x = reorder(director, Total), y = Total)) +
  geom_col(fill = "#5dc1b9") +
  coord_flip() +
  ggtitle("Netflix", "Top 10 directress/ directors creating Netflix Content") +
  geom_label(aes(x = reorder(director, Total), y = Total, label = Total)) +
  labs(x = "Directress / Director", y = "Total Content created") +
  theme_minimal()
graph4
```

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>

We can see that the top directors in Netflix are Jan Suter with 21 titles and Raúl Campos with 19 titles. Both of them created many of these titles together, so for this reason the data was splitted.


#### 5.4.  What is the trend of TV Shows and Movies over the years?

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

graph5 <- data %>%
  group_by(year=floor_date(date_added, "year"), type) %>%
  filter(year<"2021-01-01") %>%
  count() %>%
  ggplot() + geom_line(aes(x = year, y = n, group = type, color = type)) +
  ggtitle("Netflix", "Trend of Movies and TV Shows added per year") +
  labs(x = "Year", y = "Total Count") +
  theme_minimal()
graph5
```

```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
#graph5 <- data %>% 
# group_by(year=floor_date(date_added, "year"), type)


#ggplot(graph5, aes(x = year, fill = type)) + geom_bar() + #ggtitle("Netflix", "Trend of Movies and TV Shows added per year") +   #labs(x = "Years", y = "Total Content added") +
#theme_minimal()
```

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>

We can see that the trend of content added is increasing, especially from 2016 onward. We see that the highest peak was achieved in 2019. It can be also noticed how fast the amount of Movies on Netflix overcame the amount of TV Shows. 


#### 5.5 What is the distribution of duration of the seasons in TV Shows and the duration of movies?
```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
data_movie <- data %>% 
  filter(type== "Movie")
data_movie$duration<-as.character(data_movie$duration)
temp<-unlist(strsplit(data_movie$duration, " "))
temp<-temp[temp != "min"]
data_movie$durationNum<-as.numeric(temp)
#round(mean(data_movie$durationNum))

data_show <- data %>% 
  filter(type== "TV Show")
data_show$duration<-as.character(data_show$duration)
temp<-unlist(strsplit(data_show$duration, " "))
temp<-temp[temp != "Season"]
temp<-temp[temp != "Seasons"]
data_show$durationNum<-as.numeric(temp)
#round(mean(data_show$durationNum))
```
- *Movies*
```{r, collapse=FALSE, echo=FALSE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

graph6 <-ggplot(data_movie) + 
  geom_histogram(binwidth = 10, aes(x = durationNum), fill = "#5dc1b9") +
  labs(title = 'Time Duration Distribution of Movies',
       subtitle = 'in minutes')+
  labs(x = "Duration", y = "Frecuency") +
  theme_minimal()
graph6

```

Does the movie duration follow a normal distribution?  If we are confident that our data are nearly normal, that opens the door to many powerful statistical methods. Here we’ll use the graphical tools of R to assess the normality of our data.

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

params <- data_movie %>%
    summarize(mean = mean(durationNum), sd = sd(durationNum))
qq <- data_movie %>%
    ggplot(aes(sample = durationNum)) +
    geom_qq(dparams = params) +
    geom_abline()
qq

ad.test(data_movie$durationNum)

```

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>
A data set that is nearly normal will result in a probability plot where the points closely follow the line. Any deviations from normality leads to deviations of these points from the line. Based on this, the variable is not normal, and it appears to be right skewed.

Also, the p-value was checked, p-value < 0.05 means not normal

- *TV Shows*

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}

graph7 <- ggplot(data_show) + 
  geom_histogram(binwidth = 1, aes(x = durationNum), fill = "#5dc1b9") +
  labs(title = 'Distribution of TV Shows Seasons',
       subtitle = 'by Seasons')+
  labs(x = "Number of seasons", y = "Frecuency") +
  theme_minimal()
graph7

ad.test(data_show$durationNum)

```

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>
We can see that most of the TV shows that Netflix offers only have one season. Also, the distribution is not normal, as we can see in the histogram and with the p-value. The p value in this case is less than 0.05 (2.2e-16). Since the p value is low, we reject the null hypotheses that the data are from a normal distribution.


#### 5.6.  What are the Top 10 long lasting movies in Netflix? What are the top 10 long lasting Tv Shows in Netflix?

- *Movies*

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph8 <- data_movie %>% 
 arrange(desc(durationNum)) %>% 
  top_n(10, durationNum)  %>%
  ggplot(aes(x = reorder(title, durationNum), y = durationNum)) +
  geom_col(fill = "#5dc1b9") +
  coord_flip() +
  ggtitle("Netflix", "Top 10 Movies Duration") +
  labs(x = "Movie", y = "Total Minutes") +
  theme_minimal()
graph8
```

- *TV Shows*

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph9 <- data_show %>% 
 arrange(desc(durationNum)) %>% 
  top_n(10, durationNum)  %>%
  ggplot(aes(x = reorder(title, durationNum), y = durationNum)) +
  geom_col(fill = "#5dc1b9") +
  coord_flip() +
  ggtitle("Netflix", "Top 10 TV Shows Duration") +
  labs(x = "TV Shows", y = "Total Seasons") +
  theme_minimal()
graph9

```

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>

We can see that the trend of content added is increasing, especially from 2016 onward. We see that the highest peak was achieved in 2019. It can be also noticed how fast the amount of Movies on Netflix overcame the amount of TV Shows.


### <a name="point-6"></a>6.    Inference


#### 6.1. Is there a relationship between the Release Year and Duration in Movies? And the number of seasons?


- *Movie*
```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph10 <-data_movie %>% 
ggplot( aes(x = release_year, 
           y = durationNum)) +
  geom_point(color= "cornflowerblue") +
  geom_smooth(method = "lm", 
              color = "yellow")+
  theme_minimal() +                                  
  ggtitle("Netflix", "Release Year VS Movie Duration") +
  labs(x = "Release Year", y = "Duration")
graph10

cor(data_movie$release_year,data_movie$durationNum)
```
Based on that correlation coefficient, linear relationship between the two variables is low.

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
lm1 <- lm(release_year~ durationNum, data =data_movie)
summary(lm1)$r.squared
```
4,1% of time duration can be explained by the release year

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>
There is no linear relationship at all for time duration in the movies and the release year. Firstly, the correlation coefficient is low (0,2), and secondly, the r-square is 4,1%, so this means that only 4,1% of time duration can be explained by the release year.

- *TV Shows*

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph10 <-data_show %>% 
ggplot( aes(x = release_year, 
           y = durationNum)) +
  geom_point(color= "cornflowerblue") +
  geom_smooth(method = "lm", 
              color = "yellow")+
  theme_minimal() +                                  
  ggtitle("Netflix", "Release Year VS TV Show Duration") +
  labs(x = "Release Year", y = "Duration")
graph10

cor(data_show$release_year,data_show$durationNum)
```
Based on that correlation coefficient, linear relationship between the two variables is low (-0.01)

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
lm1 <- lm(release_year~ durationNum, data =data_show)
summary(lm1)$r.squared
```
8,3% of time duration can be explained by the release year

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>
There is no linear relationship at all for time duration in the TV Show and the release year. Firstly, the correlation coefficient is low (-0,1), and secondly, the r-square is 8,3%, so this means that only 8,3% of season duration can be explained by the release year.


#### 6.2. Is there a relationship between the Country and Duration in Movies? And the number of seasons?


To simplify the analysis we are going to use top countries creating the content, which are United States, India, United Kingdom, Canada, Spain, Egypt, Turkey, Philippines, Japan, France

- *Movies*

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
countries <- c("United States", "India","United Kingdom", "Canada", "Spain", "Egypt", "Turkey", "Philippines","Japan", "France")

graph11<- data_movie %>%
filter(country %in% countries)

graph11 %>%
  mutate(country = reorder(country, durationNum, FUN = mean)) %>%    # reorder
  ggplot(aes(country, durationNum, fill = country)) +    # color by continent
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Netflix", "Country VS Movie Duration") +
  labs(x = "Country", y = "Movie Duration")

graph11 %>%
filter(country %in% countries)  %>%
group_by(country) %>%
  summarise(
    size = n(),
    mean = mean(durationNum, na.rm = TRUE),
    sd = sd(durationNum, na.rm = TRUE)
  )

# Compute the analysis of variance
anova_country <- aov(durationNum ~ country, data = graph11)
# Summary of the analysis
summary(anova_country)
``` 

<p style = 'color : teal;font-size:18px'><u>Insights </u></p>

Hypothesis: the time duration of movies are the same among the countries.

The P-Value is very small (< 0.05) and therefore we reject the null hypothesis.  It means that the difference of time duration across the countries selected is statistically significant.

- *TV Shows*

```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
countries2 <- c("United States", "India","United Kingdom", "Canada", "Spain", "South Korea", "Taiwan", "Australia","Japan", "France")

graph12<- data_show %>%
filter(country %in% countries2)

graph12 %>%
  mutate(country = reorder(country, durationNum, FUN = mean)) %>%    # reorder
  ggplot(aes(country, durationNum, fill = country)) +    # color by continent
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Netflix", "Country VS Movie Duration") +
  labs(x = "Country", y = "Movie Duration")

graph12 %>%
filter(country %in% countries2)  %>%
group_by(country) %>%
  summarise(
    size = n(),
    mean = mean(durationNum, na.rm = TRUE),
    sd = sd(durationNum, na.rm = TRUE)
  )

# Compute the analysis of variance
anova_country <- aov(durationNum ~ country, data = graph12)
# Summary of the analysis
summary(anova_country)
``` 

<p style = 'color : teal;font-size:18px'><u>Insights </u></p> 

<u>Hypothesis:</u> the time duration of TV Shows are the same among the countries.

The P-Value is very small (< 0.05) and therefore we reject the null hypothesis.  It means that the difference of time duration across the countries selected is statistically significant. Also, thanks to the boxplot, we can see there are several outliers. In the ANOVA test a significant p-value indicates that means in some countries are different, though it doesn`t show, which pairs of countries are.


#### 6.3. Is there a relationship between the Genre and Duration in Movies? And the number of seasons? 


```{r, collapse=FALSE, echo=TRUE, results='markup', error=FALSE, message=FALSE, warning=FALSE}
graph13 <- data_movie %>%
  mutate(listed_in = strsplit(as.character(listed_in), ", ")) %>%
  unnest(listed_in) %>% 
  group_by(listed_in,durationNum) 

graph13 %>%
  mutate(listed_in = reorder(listed_in, durationNum, FUN = mean)) %>%
  ggplot(aes(listed_in, durationNum, fill = listed_in)) +   
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Netflix", "Genre VS Movie Duration") +
  labs(x = "Genre", y = "Movie Duration")

graph13 %>%
group_by(listed_in) %>%
  summarise(
    size = n(),
    mean = mean(durationNum, na.rm = TRUE),
    sd = sd(durationNum, na.rm = TRUE)
  )

# Compute the analysis of variance
anova_genre <- aov(durationNum ~ listed_in, data = graph13)
# Summary of the analysis
summary(anova_genre)
layout(matrix(1:4, 2, 2))

plot(anova_genre)
``` 

<p style = 'color : teal;font-size:18px'><u>Insights </u></p> 

<u>Hypothesis:</u> the time duration of the movies are the same among the genres.


The P-Value is very small (< 0.05) and therefore we reject the null hypothesis.  It means that at least two of the means are different,  the difference in movie duration between the genres is statistically significant.In the ANOVA test a significant p-value indicates that means in some genres are different, though it doesn`t show, which pairs of genres are.

### <a name="point-7"></a>7.    Conclusions

The data was scraped and manipulated accordingly for the analysis. The data was then reviewed graphically to determine what is the general trend of movies and tv show in Netflix , using scatter plots, line chart, boxplot and bar charts.

- The 69,1% of the content from Netflix are movies and the 30.9% are TV Shows

- The top 3 countries creating Movie content for Netflix are United States, United Kingdom and Japon and top 3 countries creating TV Show content are United States, India and United Kingdom. United States is the most favorite country to produce Netflix content for movies and TV Shows

- The most favorite directors creating content for Netflix are Jan Suter with 21 titles and Raúl Campos with 19 titles.

- The long lasting movie is  Black Mirror Bandersnatch with 312 minutes and the long lasting TV Show in Netflix is Grey's Anatomy with 17 seasons
- 
There is no linear relationship at all for time duration in the Movies and TV Shows and the release year. Firstly, the correlation coefficient is low (0,2 and -0,1), and secondly, the r-square is also low (4,1% and 8,3)

- The difference of time duration across the countries selected is statistically significant. To find which countries are statistically significant, a post hoc test can be conducted . The same happens with the genres


### <a name="point-8"></a>8.    References

- https://plotly.com/r/plotly-fundamentals/
- https://doyouevendata.github.io/Beautifying-plotly-graphs-in-R/
- http://haozhu233.github.io/kableExtra/awesome_table_in_html.html
